A Noncomprehensive Annotated Bibliography for Analysing the General Porous Medium Equation

### 2014-11-25 trygve_b_written_assignment4.tex
Changed title

\title{Written assignment 4 in SPRÅK3501}
\author{Trygve Bærland}
\maketitle
\section*{Introduction:}
In my project I will consider a generalisation of the Porous Medium Equation, and specifically try to construct a numerical method that converges to a, in some sense, unique solution.

@@

Indeed, the mathematical knowledge expected of the reader in this paper will indubitably cast any critique I may impart in a bad light, but in any case there are structural issues here that I feel competent enough to address. The previously mentioned confusion arises from such structural acrobatics as putting a proof of a minor result in the middle of a larger proof, and have almost no interstitial discussions. Especially the latter of these editorial decisions makes the paper extremely difficult to read. With no discernible "narrative"\footnote{Running thread, or whatever the english translation of the norwegian idiom "rød tråd" is.} the writer seems to expect a whole lot on the reader's concentration, focus, and ability to maintain both.

>>>>

\title{A Noncomprehensive Annotated Bibliography for Analysing the General Porous Medium Equation}
\author{Trygve Bærland}
\maketitle
\section*{Introduction:}
In my project I will consider a generalisation of the Porous Medium Equation, and specifically try to construct a numerical method that converges to a, in some sense, unique solution.

@@

Indeed, the mathematical knowledge expected of the reader in this paper will indubitably cast any critique I may impart in a bad light, but in any case there are structural issues here that I feel competent enough to address. The previously mentioned confusion arises from such structural acrobatics as putting a proof of a minor result in the middle of a larger proof, and have almost no interstitial discussions. Especially the latter of these editorial decisions makes the paper extremely difficult to read. With no discernible running theme the writer seems to expect a whole lot on the reader's concentration, focus, and ability to maintain both.
